Tailoring Differentially Private Bayesian Inference to Distance Between Distributions

### 2018-10-23 Arxiv/main.tex
update proof

\section{Introduction}
\label{sec_intro}
Data analysis techniques are broadly used in various applications in different areas to improve their service, including disease-medicine service, financial service, location service, social network and so on. In order to provide a better service, large of data are collected from users for analysis. As a consequence, the data privacy came to be a critical issue in all data analysis algorithms. Sensitivity information in data can be revealed through the analysis results. The key challenge here is to release a private analysis results, from which adversary cannot observe individual's sensitive information in data.

Plenty of work have been developed to solve this issue(), They guranteed the privacy in specific data analysis algorithms.

@@

\noindent \textbf{Main contributions.}
\begin{itemize}
	\item We designed a differentially private Bayesian inference mechanism based on the standard exponential mechanism.
	\item The accuracy is improved by two ways: 1) calibrating noise to the sensitivity of a
         metric over distributions (e.g. Hellinger distance ($\hellinger$), $f$-divergences, etc\dots).
	\item We implemented the new proposed mechanism and other art-of-state mechanisms, comparing the performance in terms of accuracy and efficiency.
\end{itemize}

@@

\section{Preliminaries}
\label{sec_Pre}

@@

A randomized mechanism $\mathcal{M}: \mathcal{X} \rightarrow \mathcal{Y}$ is differential privacy, iff for any adjacent input $\dataobs, \dataobs' \in \mathcal{X}$, a metric $H$ over $\mathcal{Y}$ and a $B \subseteq H(\mathcal{Y})$, $\mathcal{M}$ satisfies:
\begin{equation*}
\mathbb{P}[H(\mathcal{M}(\dataobs)) \in B] = e^\epsilon \mathbb{P}[H(\mathcal{M}(\dataobs')) \in B],
\end{equation*}
where $\dataobs = (x_i)_{i = 1}^n$ if there is only one $j$ that $x_j \neq x'_j$ and $x_i = x'_i$ for $i = 1, 2, \cdots, n; i \neq j$. 
\end{definition}

@@

A randomized mechanism $\mathcal{M}: \mathcal{X} \rightarrow \mathcal{Y}$ is differential privacy, iff for any adjacent input $\dataobs, \dataobs' \in \mathcal{X}$, a metric $H$ over $\mathcal{Y}$ and a $B \subseteq H(\mathcal{Y})$, $\mathcal{M}$ satisfies:
\begin{equation*}
\mathbb{P}[H(\mathcal{M}(\dataobs)) \in B] = e^\epsilon \mathbb{P}[H(\mathcal{M}(\dataobs')) \in B] + \delta,
\end{equation*}
vwhere $\dataobs = (x_i)_{i = 1}^n$ if there is only one $j$ that $x_j \neq x'_j$ and $x_i = x'_i$ for $i = 1, 2, \cdots, n; i \neq j$. 
\end{definition}

@@

Also, in previous works, the accuracy of the posterior was measured again with respect to $\ell_1$ norm. That is, an upper bound was given on
\[
  \Pr[|\alpha - \tilde\alpha| + |\beta - \tilde\beta |\geq \gamma ]
\]
where $(\alpha, \beta), (\tilde\alpha,\tilde\beta)$ are as defined above. However, this accuracy metric is meaningless when the object released is a distribution rather than a numerical value, and distribution metrics such as $f$-divergence, Hellinger distance, etc. come into mind overtly when we are measuring distance between distributions.

In this work we will use a metric based on a different norm (a distribution metric) to compute the sensitivity
and provide guarantees on the accuracy. 
Specifically, we will use the Hellinger distance $\hellinger(\cdot,\cdot)$:
Given two beta distributions
$\boldsymbol{\beta}_1=\betad(\alpha_1, \beta_1),$ and $\boldsymbol{\beta}_2=\betad(\alpha_2, \beta_2)$ the following equality holds 
\[
  \hellinger(\boldsymbol{\beta}_1, \boldsymbol{\beta}_2)=
  \sqrt{1 - \frac{\betaf(\frac{\alpha_1 + \alpha_2}{2}, \frac{\beta_1 + \beta_2}{2})}{\sqrt{\betaf(\alpha_1,\beta_1)\betaf(\alpha_2,\beta_2)}}}
\]

Our choice to use Hellinger distance is motivated by three facts:
\begin{itemize}
\item It simplifies calculations in the case of the probabilistic models considered here.
\item It also automatically yields bounds on the total variation distance, which represents also the maximum advantage
an unbounded adversary can have in distingishing two distributions. 
\item The accuracy can be improved by using a smooth bound on Hellinger distance's local sensitivity. As shown in Fig. \ref{fig_sensitivity}, taking advantage of the gap between the global sensitivity and local sensitivity, we can improve the accuracy a lot by applying a smooth upper bound on local sensitivity.
\begin{figure}[ht]
\centering
\includegraphics[width=0.35\textwidth]{sensitivity_2d.eps}
\caption{{Sensitivity of $\hellinger$}}
\label{fig_sensitivity}
\end{figure}
\end{itemize}

@@

\subsection{ $\hexpmech$: Smoothed Hellinger Distance Based Exponential Mechanism}
\label{subsec_hexpmech}

@@

By setting the $\gamma$ as $\ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta}{2 (n + 1)})})$, $\hexpmech$ is $(\epsilon, \delta) -$differentially private.

\section{Privacy Proof}
The differential privacy property of $\hexpmech$ is proved based on the holds of the two properties: \emph{sliding property} and \emph{dilation property}.

\subsection{Sliding Property of $\hexpmech$}
\begin{lem}
Given $\hexpmech(x)$ calibrated on the smooth sensitivity. Let $\lambda = f(\epsilon,
\delta)$, $\epsilon\geq 0$ and $|\delta| < 1$. Then, the following \emph{sliding property} holds:
\begin{equation*}
\underset{r \thicksim \hexpmech(x)}{Pr}[u(r,x) = \hat{s}]
\leq
e^{\frac{\epsilon}{2}} \underset{r \thicksim \hexpmech(x)}{Pr}[u(r,x) = (\Delta + \hat{s})] + \frac{\delta}{2},
\end{equation*}

@@

In what follows, we will use a correspondence between the probability
 $\underset{z \thicksim \hexpmech(x)}{Pr}[z = r]$ of every
 $r\in\candidateset$ and the probability 
 $\underset{z \thicksim \hexpmech(x)}{Pr}[\hellinger(\bysinfer(x),z) =
 \hellinger(\bysinfer(x),r)]$ for the utility score for $r$. In particular, for every
 $r\in\candidateset$ we have:

$$
\underset{z \thicksim \hexpmech(x)}{Pr}[z = r]=
\frac{1}{2}\Big (\underset{z \thicksim \hexpmech(x)}{Pr}[\hellinger(\bysinfer(x),z) =
 \hellinger(\bysinfer(x),r)]\Big )
$$

To see this, it is enough to notice that: $\underset{z \thicksim \hexpmech(x)}{Pr}[z = r]$ is proportional too $\hellinger(\bysinfer(x),r)$, i.e., $u(x,z)$. We can derive, if $u(r,x) = u(r',x)$ then $\underset{z \thicksim \hexpmech(x)}{Pr}[z = r] = \underset{z \thicksim \hexpmech(x)}{Pr}[z = r']$. We assume the number of candidates $z \in \mathcal{R}$ that satisfy $u(z,x) = u(r,x)$ is $|r|$, we have  $\underset{z \thicksim \hexpmech(x)}{Pr}[u(z,x) = u(r,x)] = |r| \underset{z \thicksim \hexpmech(x)}{Pr}[z = r]$. Because Hellinger distance  $\hellinger(\bysinfer(x),z)$ is axial symmetry, where the $\bysinfer(x)$ is the symmetry axis. It can be infer that $|z| = 2$ for any candidates, apart from the true output, i.e., $\underset{z \thicksim \hexpmech(x)}{Pr}[u(z,x) = u(r,x)] = 2 \underset{z \thicksim \hexpmech(x)}{Pr}[z = r]$. This parameter can be eliminate in both sides in proof.

@@

\begin{equation*}
\begin{split}
\frac{exp(\frac{\epsilon (\hat{s} + \Delta)}{2 S(x)})}{NL(x)} \cdot e^{\frac{- \epsilon \Delta}{2 S(x)}}
& \leq \frac{exp(\frac{\epsilon (\hat{s} + \Delta)}{2 S(x)})}{NL(x)} \cdot e^{\frac{\epsilon}{2}}\\
&  =  e^{\frac{\epsilon}{2}} \underset{z \thicksim \hexpmech(x)}{Pr}[u(r,x) = (\Delta + \hat{s})] \leq RHS\\
\end{split}
\end{equation*}

@@

\subsection{Dilation Property of $\hexpmech$}
\begin{lem}
for any exponential mechanism $\hexpmech(x)$, $\lambda < |\beta|$, $\epsilon$, $|\delta| < 1$ and $\beta \leq \ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta}{2 (n + 1)})})$, the dilation property holds:

\begin{equation*}
\underset{z \thicksim \hexpmech(x)}{Pr}[u(z,x) = c]
\leq
e^{\frac{\epsilon}{2}} \underset{z \thicksim \hexpmech(x)}{Pr}[u(z,x) = e^{\lambda} c] + \frac{\delta}{2},
\end{equation*}
where the sensitivity in mechanism is still smooth sensitivity as above.
\end{lem}

@@

We set the $h(c) = Pr[u(\hexpmech(x)) = c] = 2\frac{exp(\frac{\epsilon z}{2 S(x)})}{NL(x)}$.

@@

\textbf{Detail proof:}

	By simplification, we get this formula: $u(\hexpmech(x)) \leq \frac{S(x)}{(1 - e ^ {\lambda})}$
\begin{itemize}
	\item $\lambda < 0$

@@

		In beta-binomial model, $|\candidateset| = n + 1$, apply this bound to eq. \ref{eq_dilation_case2}:
		\begin{equation*}
		\begin{split}
		Pr[u(\hexpmech(x)) \leq \frac{S(x)}{(1 - e ^ {\lambda})}] 
		& = (n + 1)exp(\frac{\epsilon S(x)}{(1 - e ^ {\lambda})}/2 S(x))\\
		& = (n + 1)exp(\frac{\epsilon}{2 (1 - e ^ {\lambda})})\\
		\end{split}
		\end{equation*}

@@

@@

\subsection{$(\epsilon, \delta)-$Differential Privacy}
\begin{lem}
\label{lem_hexpmech_privacy}
$\hexpmech$ is $(\epsilon, \delta)$-differential privacy.
\end{lem}

\begin{proof}
of Lemma \ref{lem_hexpmech_privacy}: For all neighboring $x, y \in D^n$ and all sets $\mathcal{S}$, we need to show that:
\begin{equation*}
\underset{z \thicksim \hexpmech(x)}{Pr}[ z \in \mathcal{S}] \leq e^{\epsilon} \underset{z \thicksim \hexpmech(y)}{Pr}[z \in \mathcal{S}] + \delta. 
\end{equation*}
Given that $2\Big( \underset{z \thicksim \hexpmech(x)}{Pr}[ z \in \mathcal{S}]\Big) = \underset{z \thicksim \hexpmech(x)}{Pr}[ u(x,z) \in \mathcal{U}]$, let $\mathcal{U}_1 = \frac{u(y,z) - u(x,z)}{S(x)}$, $\mathcal{U}_2 = \mathcal{U} + \mathcal{U}_1$ and $\mathcal{U}_3 = \mathcal{U}_2 \cdot \frac{S(x)}{S(y)} \cdot \ln(\frac{NL(x)}{NL(y)})$. Then,

\begin{equation*}
\begin{split}
2\Big( \underset{z \thicksim \hexpmech(x)}{Pr}[ z \in \mathcal{S}]\Big)
& = \underset{z \thicksim \hexpmech(x)}{Pr}[ u(x,z) \in \mathcal{U}]\\
& \leq e^{\epsilon / 2} \cdot \underset{z \thicksim \hexpmech(x)}{Pr}[ u(x,z) \in \mathcal{U}_2]\\
& \leq e^{\epsilon} \cdot \underset{z \thicksim \hexpmech(x)}{Pr}[ u(x,z) \in \mathcal{U}_3] + e^{\epsilon/2} \cdot \frac{\delta'}{2}\\
& = e^{\epsilon} \cdot \underset{z \thicksim \hexpmech(y)}{Pr}[ u(y,z) \in \mathcal{U}] + \delta = 2\Big( e^{\epsilon} \cdot \underset{z \thicksim \hexpmech(x)}{Pr}[ z \in \mathcal{S}] \Big) + \delta\\
\end{split}
\end{equation*}

The first inequality holds by the sliding property, since the $\mathcal{U}_1 \geq -S(x)$. The second inequality holds by the dilation property, since $\frac{S(x)}{S(y)} \cdot \ln(\frac{NL(x)}{NL(y)}) \leq 1 - \frac{\epsilon}{2 \ln (\frac{\delta}{2 (n + 1)})}$.

@@

\subsection{Accuracy Bound for Laplace Mechanism}
\label{subsec_accuracy_lap}
Accuracy bound for Laplace mechanism is provided by its probability density function:
\begin{equation*}
Pr[|Y| \geq t] = e^{- \frac{t}{b}},
\end{equation*}
where $Y \sim Lap(b)$, $b = \frac{\Delta \bysinfer}{\epsilon}$ in our case.

@@

\subsection{Accuracy Bound for Exponential Mechanism}
\label{subsec_accuracy_global}
The accuracy bound of exponential mechanism is provided in \cite{dwork2014algorithmic} as:
\begin{equation*}
Pr[u(\expmech{}{x}{u}{\candidateset}) \leq c] 
		 \leq \frac{|\mathcal{R}|exp(\frac{\epsilon c}{2 GS})}{|\mathcal{R}_{OPT}| exp(\frac{\epsilon OPT_{u(x)}}{2 GS})},
\end{equation*}
where $|R|$ is the size of the candidate set, $OPT$ is the optimal candidates, $|R_{OPT}|$ is the number of optimal candidates.

@@

>>>>

\section{Introduction}
\label{sec_intro}
Data analysis techniques are broadly used in various applications in different areas to improve their services, including disease-medicine service, financial service, location service, social network and so on. In order to provide a better service, large of data are collected from users for analysis. As a consequence, the data privacy came to be a critical issue. Sensitivity information in data can be revealed through the analysis results. The key challenge here is to release a private analysis results, from which adversary cannot observe individual's sensitive information in data.

Plenty of work have been developed to solve this issue, guaranteeing the privacy in specific data analysis algorithms. They achieved the $\epsilon-$differential privacy by adopting either Laplace mechanism or achieved the $(\epsilon, \delta)-$differential privacy. But they are not giving better accuracy than the differential privacy mechanism itself. Here, we are proposing mechanism with better accuracy.

@@

\noindent \textbf{Main contributions.}
\begin{itemize}
	\item We designed a differentially private Bayesian inference mechanism based on the standard exponential mechanism.
	\item The accuracy is improved by two ways: 1) calibrating noise to the sensitivity of a
         metric over distributions (e.g. Hellinger distance ($\hellinger$), $f$-divergences, etc\dots). 2) Using a smooth upper bound on the local sensitivity and scale the noise to this smooth bound rather than global sensitivity, to improve the mechanism accuracy.
	\item We implemented the new proposed mechanism and other art-of-state mechanisms, comparing the performance in terms of accuracy and efficiency.
\end{itemize}

@@

\section{Preliminaries}
\label{sec_background}

@@

A randomized mechanism $\mathcal{M}: \mathcal{X} \rightarrow \mathcal{Y}$ is differential privacy, iff for any adjacent input $\dataobs, \dataobs' \in \mathcal{X}$, a metric $H$ over $\mathcal{Y}$ and a $B \subseteq H(\mathcal{Y})$, $\mathcal{M}$ satisfies:
\begin{equation*}
\mathbb{P}[H(\mathcal{M}(\dataobs)) \in B] = e^\epsilon \mathbb{P}[H(\mathcal{M}(\dataobs')) \in B],
\end{equation*}
where $\dataobs = (x_i)_{i = 1}^n$ and $\dataobs = (x'_i)_{i = 1}^n$ is adjacent if there is only one $j$ that $x_j \neq x'_j$ and $x_i = x'_i$ for $i = 1, 2, \cdots, n; i \neq j$. 
\end{definition}

@@

A randomized mechanism $\mathcal{M}: \mathcal{X} \rightarrow \mathcal{Y}$ is differential privacy, iff for any adjacent input $\dataobs, \dataobs' \in \mathcal{X}$, a metric $H$ over $\mathcal{Y}$ and a $B \subseteq H(\mathcal{Y})$, $\mathcal{M}$ satisfies:
\begin{equation*}
\mathbb{P}[H(\mathcal{M}(\dataobs)) \in B] = e^\epsilon \mathbb{P}[H(\mathcal{M}(\dataobs')) \in B] + \delta,
\end{equation*}
vwhere $\dataobs = (x_i)_{i = 1}^n$ and $\dataobs = (x'_i)_{i = 1}^n$ is adjacent if there is only one $j$ that $x_j \neq x'_j$ and $x_i = x'_i$ for $i = 1, 2, \cdots, n; i \neq j$. 
\end{definition}

@@

However, in previous works, the accuracy of the posterior was measured again with respect to $\ell_1$ norm. That is, an upper bound was given on
\[
  \Pr[|\alpha - \tilde\alpha| + |\beta - \tilde\beta |\geq \gamma ]
\]
where $(\alpha, \beta), (\tilde\alpha,\tilde\beta)$ are as defined above. This accuracy metric is meaningless when the results released are distributions rather than numerical values. In contrast, distribution metrics such as $f$-divergence, Hellinger distance, etc. come into mind overtly when we are measuring distance between distributions. This gives us motivation on using a different norm (a distribution metric) to compute the sensitivity
and provide guarantees on the accuracy.

Specifically, we will use the Hellinger distance $\hellinger(\cdot,\cdot)$:
Given two beta distributions
$\boldsymbol{\beta}_1=\betad(\alpha_1, \beta_1),$ and $\boldsymbol{\beta}_2=\betad(\alpha_2, \beta_2)$ the following equality holds 
\[
  \hellinger(\boldsymbol{\beta}_1, \boldsymbol{\beta}_2)=
  \sqrt{1 - \frac{\betaf(\frac{\alpha_1 + \alpha_2}{2}, \frac{\beta_1 + \beta_2}{2})}{\sqrt{\betaf(\alpha_1,\beta_1)\betaf(\alpha_2,\beta_2)}}}
\]

Our choice to use Hellinger distance is motivated by three facts:
\begin{itemize}
\item It simplifies calculations in the case of the probabilistic models considered here.
\item It also automatically yields bounds on the total variation distance, which represents also the maximum advantage
an unbounded adversary can have in distingishing two distributions. 
\item The accuracy can be improved by using a smooth bound on Hellinger distance's local sensitivity. As shown in Fig. \ref{fig_sensitivity}, taking advantage of the gap between the global sensitivity and local sensitivity, we can improve the accuracy by applying a smooth upper bound on local sensitivity instead of using global sensitivity.
\begin{figure}[ht]
\centering
\includegraphics[width=0.35\textwidth]{sensitivity_2d.eps}
\caption{{Sensitivity of $\hellinger$}}
\label{fig_sensitivity}
\end{figure}
\end{itemize}

@@

\subsection{$\hexpmech$: Smoothed Hellinger Distance Based Exponential Mechanism}
\label{subsec_hexpmech}

@@

By setting the $\gamma$ as $\ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta}{2 (n + 1)})})$ (or $\ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta}{2 |\candidateset|})})$ when generalized to Dirichlet-multinomial System), $\hexpmech$ is $(\epsilon, \delta) -$differentially private.

\section{Privacy Analysis}

\subsection{Privacy Analysis for Baseline Mechanisms}
In baseline mechanisms, \emph{exponential mechanism}, \emph{Laplace mechanism}, \emph{improved Laplace mechanism} are $\epsilon-$differential privacy provided by \citet{dwork2014algorithmic}. The \emph{exponential mechanism with local sensitivity} is non-differential privacy, also from \citet{dwork2014algorithmic}.

\subsection{Privacy Analysis for $\hexpmech$}

The differential privacy property of $\hexpmech$ is proved based on the holds of the two properties: \emph{sliding property} and \emph{dilation property}.\\

\noindent \textbf{Sliding Property of $\hexpmech$}
\begin{lem}
Given $\hexpmech(x)$ calibrated on the smooth sensitivity. Let $\lambda = f(\epsilon,
\delta)$, $\epsilon\geq 0$ and $|\delta| < 1$. Then, the following \emph{sliding property} holds:
\begin{equation*}
\underset{r \thicksim \hexpmech(x)}{Pr}[u(r,x) = \hat{s}]
\leq
e^{\frac{\epsilon}{2}} \underset{r \thicksim \hexpmech(x)}{Pr}[u(r,x) = (\Delta + \hat{s})] + \frac{\delta}{2},
\end{equation*}

@@

In what follows, we will use a correspondence between the probability
 $\underset{z \thicksim \hexpmech(x)}{Pr}[z = r]$ of every
 $r\in\candidateset$ and the probability 
 $\underset{z \thicksim \hexpmech(x)}{Pr}[\hellinger(\bysinfer(x),z) =
 \hellinger(\bysinfer(x),r)]$ for the utility score for $r$. In Beta-binomial system, because of the property of beta function, the order of parameters in Beta distribution doesn't matter when computing the Hellinegr distance. More specifically, for 3 different beta distributions $\betad(\alpha_0, \beta_0)$, $\betad(\alpha_1, \beta_1)$ and $\betad(\alpha_2, \beta_2)$, $\hellinger(\betad(\alpha_0, \beta_0),\betad(\alpha_1, \beta_1)) = \hellinger(\betad(\alpha_0, \beta_0),\betad(\alpha_2, \beta_2))$ iff $\alpha_2 = \beta_1$,  $\alpha_1 = \beta_2$ and $\alpha_0 + \alpha_1 = \beta_0 + \beta_2$ and $\alpha_0 + \alpha_2 = \beta_0 + \beta_1$.

 From this, we can derive that there are either only one or two candidates in $\candidateset$ can have the same score, i.e., for every $r \in \candidateset$ we have: $
 \underset{z \thicksim \hexpmech(x)}{Pr}[z = r]$ either 
 $$
 =\frac{1}{2}\Big (\underset{z \thicksim \hexpmech(x)}{Pr}[\hellinger(\bysinfer(x),z) =
 \hellinger(\bysinfer(x),r)]\Big )
 $$ or 
 $$
 =\underset{z \thicksim \hexpmech(x)}{Pr}[\hellinger(\bysinfer(x),z) = \hellinger(\bysinfer(x),r)]
 $$
 % proportional too $\hellinger(\bysinfer(x),r)$, i.e., $u(x,z)$. We can derive, if $u(r,x) = u(r',x)$ then $\underset{z \thicksim \hexpmech(x)}{Pr}[z = r] = \underset{z \thicksim \hexpmech(x)}{Pr}[z = r']$. 
 We assume the number of candidates $z \in \mathcal{R}$ that satisfy $\hellinger(\bysinfer(x),z) = \hellinger(\bysinfer(x),r)$, i.e. $u(z,x) = u(r,x)$ is $|z|$, then  $\underset{z \thicksim \hexpmech(x)}{Pr}[u(z,x) = u(r,x)] = |z| \underset{z \thicksim \hexpmech(x)}{Pr}[z = r]$. It can be infer that $|z| = 2$ or $|z| = 1$, i.e., $\underset{z \thicksim \hexpmech(x)}{Pr}[u(z,x) = u(r,x)] = 2 \underset{z \thicksim \hexpmech(x)}{Pr}[z = r]$ or $\underset{z \thicksim \hexpmech(x)}{Pr}[z = r]$.

 The same way in Dirichlet-multinomial system. By combination and permutation, $|z|$ can take value of 1 or 3 or 6 in 3 dimensionality, and trivially in higher dimensions.

 In Beta-binomial system, let $R_1, R_2 \subset \candidateset$ be a partition of $\candidateset$, where every $z \in R_1$ has a distinct score, i.e., $|z| = 1$ and $z \in R_2$ has another $z' \in R_2$ with the same score, i.e., $|z| = 2$. The proofs are given by parts:

 \begin{itemize}
 	\item for $r \in R_1$:

@@

		\begin{equation*}
		\begin{split}
		\frac{exp(\frac{\epsilon (\hat{s} + \Delta)}{2 S(x)})}{NL(x)} \cdot e^{\frac{- \epsilon \Delta}{2 S(x)}}
		& \leq \frac{exp(\frac{\epsilon (\hat{s} + \Delta)}{2 S(x)})}{NL(x)} \cdot e^{\frac{\epsilon}{2}}\\
		&  =  e^{\frac{\epsilon}{2}} \underset{z \thicksim \hexpmech(x)}{Pr}[u(r,x) = (\Delta + \hat{s})] \leq RHS\\
		\end{split}
		\end{equation*}
	\item for $r \in R_2$: Actually is exactly the same as above by eliminating the parameter $|z|$ in both sides.
\end{itemize}

The same in Dirichlet-multinomial distribution, partitioning the $\candidateset$ by the possible value of $|z|$, the proof can be derived in the same way as above by part.

@@

\noindent \textbf{Dilation Property of $\hexpmech$}
\begin{lem}
for any exponential mechanism $\hexpmech(x)$, $\lambda < |\beta|$, $\epsilon$, $|\delta| < 1$ and $\beta \leq \ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta}{2 |\candidateset|})})$, the dilation property holds:

\begin{equation*}
\underset{z \thicksim \hexpmech(x)}{Pr}[u(z,x) = c]
\leq
e^{\frac{\epsilon}{2}} \underset{z \thicksim \hexpmech(x)}{Pr}[u(z,x) = e^{\lambda} c] + \frac{\delta}{2},
\end{equation*}
where the sensitivity in mechanism is still smooth sensitivity as above.

More specifically, in Beta-binomial system it is enough to take $\beta \leq \ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta}{2 (n + 1)})})$.
\end{lem}

\begin{proof}
We partition $\candidateset$ in the same way as before, $R_1, R_2$. It is enough to proof under just one partition. Without loss of generalization, we take $R_1$.

@@

We set the $h(c) = Pr[u(\hexpmech(x)) = c] = \frac{exp(\frac{\epsilon c}{2 S(x)})}{NL(x)}$.

@@

\textbf{Detail proof:}
	To show:
	\begin{equation*}
	\underset{z \thicksim \hexpmech(x)}{Pr}[u(z,x) = c]
	\leq
	e^{\frac{\epsilon}{2}} \underset{z \thicksim \hexpmech(x)}{Pr}[u(z,x) = e^{\lambda} c] + \frac{\delta}{2}
	\end{equation*}
	for $z \in R_1$.

	Let $Pr[u(\hexpmech(x)) = c] = \frac{exp(\frac{\epsilon c}{2 S(x)})}{NL(x)}$ and $Pr[u(\hexpmech(x)) = e^{\lambda} c] = \frac{exp(\frac{\epsilon e^{\lambda} c}{2 S(x)})}{NL(x)}$ by definition.

	After simplification, we need to show: $u(\hexpmech(x)) \leq \frac{S(x)}{(1 - e ^ {\lambda})}$.
	Because the sensitivity is always greater than 0, and our utility function $-\hellinger(\bysinfer(x),z)$ is smaller than zero, i.e., $u(z,x) \leq 0$, we need to consider two cases where $\lambda < 0$, and $\lambda > 0$:

\begin{itemize}
	\item $\lambda < 0$

@@

		In Beta-binomial system, $|\candidateset| = n + 1$, apply this bound to eq. \ref{eq_dilation_case2}:
		\begin{equation*}
		\begin{split}
		Pr[u(\hexpmech(x)) \leq \frac{S(x)}{(1 - e ^ {\lambda})}] 
		& = (n + 1)exp(\frac{\epsilon S(x)}{(1 - e ^ {\lambda})}/2 S(x))\\
		& = (n + 1)exp(\frac{\epsilon}{2 (1 - e ^ {\lambda})})\\
		\end{split}
		\end{equation*}

@@

		In Dirichlet-multinomial system, $\lambda$ is set as $ \leq \ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta}{2 |\candidateset|})})$ since $|\candidateset| \neq n + 1$ any more.

@@

\noindent \textbf{$(\epsilon, \delta)-$Differential Privacy of $\hexpmech$}
\begin{lem}
\label{lem_hexpmech_privacy}
$\hexpmech$ is $(\epsilon, \delta)$-differential privacy.
\end{lem}

For all neighboring $x, y \in D^n$ and all sets $\mathcal{S}$, we need to show that:
\begin{equation*}
\underset{z \thicksim \hexpmech(x)}{Pr}[ z = r] \leq e^{\epsilon} \underset{z \thicksim \hexpmech(y)}{Pr}[z = r] + \delta. 
\end{equation*}

Let partition $R_1, R_2 \subset \candidateset$ the same as above. Then we prove by part:
\begin{itemize}
	\item for $r \in R_1$:

	Given that $\underset{z \thicksim \hexpmech(x)}{Pr}[z = r] = \underset{z \thicksim \hexpmech(x)}{Pr}[u(x,z) = u(x,r)]$, let $U = u(x,r)$, $U_1 = u(y,z) - u(x,z)$, $U_2 = U + U_1$ and $U_3 = U_2 \cdot \frac{S(x)}{S(y)} \cdot \ln(\frac{NL(x)}{NL(y)})$. Then,

	\begin{equation*}
	\begin{split}
	\underset{z \thicksim \hexpmech(x)}{Pr}[ z = r]
	& = \underset{z \thicksim \hexpmech(x)}{Pr}[ u(x,z) = U]\\
	& \leq e^{\epsilon / 2} \cdot \underset{z \thicksim \hexpmech(x)}{Pr}[ u(x,z) = U_2]\\
	& \leq e^{\epsilon} \cdot \underset{z \thicksim \hexpmech(x)}{Pr}[ u(x,z) = U_3] + e^{\epsilon/2} \cdot \frac{\delta'}{2}\\
	& = e^{\epsilon} \cdot \underset{z \thicksim \hexpmech(y)}{Pr}[ u(y,z) = U] + \frac{e^{\epsilon/2} \delta'}{2} \\
	& = e^{\epsilon} \cdot \underset{z \thicksim \hexpmech(x)}{Pr}[ z = r] + \delta,
	\end{split}
	\end{equation*}
	where $\delta = \frac{e^{\epsilon/2} \delta'}{2}$.
	The first inequality holds by the sliding property, since the $U_1 \geq -S(x)$. The second inequality holds by the dilation property, since $\frac{S(x)}{S(y)} \cdot \ln(\frac{NL(x)}{NL(y)}) \leq 1 - \frac{\epsilon}{2 \ln (\frac{\delta}{2 (n + 1)})}$.

	\item for $r \in R_2$:

	Given that $2\Big( \underset{z \thicksim \hexpmech(x)}{Pr}[z = r]\Big) = \underset{z \thicksim \hexpmech(x)}{Pr}[ u(x,z) = u(x,r)]$, let $U = u(x,r)$, $U_1 = u(y,z) - u(x,z)$, $U_2 = U + U_1$ and $U_3 = U_2 \cdot \frac{S(x)}{S(y)} \cdot \ln(\frac{NL(x)}{NL(y)})$. Then,

	\begin{equation*}
	\begin{split}
	\underset{z \thicksim \hexpmech(x)}{Pr}[ z = r]
	& = 	\frac{1}{2}\Big( \underset{z \thicksim \hexpmech(x)}{Pr}[ u(x,z) = U]\Big)\\
	& \leq 	\frac{1}{2}\Big( e^{\epsilon / 2} \cdot \underset{z \thicksim \hexpmech(x)}{Pr}[ u(x,z) = U_2]\Big)\\
	& \leq 	\frac{1}{2}\Big( e^{\epsilon} \cdot \underset{z \thicksim \hexpmech(x)}{Pr}[ u(x,z) = U_3] + e^{\epsilon/2} \cdot \frac{\delta'}{2}\Big)\\
	& = 	\frac{1}{2}\Big( e^{\epsilon} \cdot \underset{z \thicksim \hexpmech(y)}{Pr}[ u(y,z) = U] + \frac{e^{\epsilon/2} \delta'}{2}\Big) \\
	& = e^{\epsilon} \cdot \underset{z \thicksim \hexpmech(x)}{Pr}[ z = r] + \delta,
	\end{split}
	\end{equation*}
	where the $\delta = \frac{e^{\epsilon/2} \delta'}{4}$.

	The first inequality holds by the sliding property, since the $U_1 \geq -S(x)$. The second inequality holds by the dilation property, since $\frac{S(x)}{S(y)} \cdot \ln(\frac{NL(x)}{NL(y)}) \leq 1 - \frac{\epsilon}{2 \ln (\frac{\delta}{2 (n + 1)})}$.
\end{itemize}

Based on two cases above, $\hexpmech$ is $(\epsilon, \delta)-$differential privacy, where $\delta$ takes the maximum value form the two cases.

Proof in Dirichlet-multinomial system can be derived in the same way by proving in parts and taking the maximum $\delta$ value of each part. 
\end{proof}

@@

\subsection{Accuracy Bound for Baseline Mechanisms}

\subsubsection{Accuracy Bound for Exponential Mechanism}
\label{subsec_accuracy_global}
The accuracy bound of exponential mechanism is provided in \cite{dwork2014algorithmic} as:
\begin{equation*}
Pr[u(\expmech{}{x}{u}{\candidateset}) \leq c] 
		 \leq \frac{|\mathcal{R}|exp(\frac{\epsilon c}{2 GS})}{|\mathcal{R}_{OPT}| exp(\frac{\epsilon OPT_{u(x)}}{2 GS})},
\end{equation*}
where $|R|$ is the size of the candidate set, $OPT$ is the optimal candidates, $|R_{OPT}|$ is the number of optimal candidates.

\subsubsection{Accuracy Bound for Laplace Mechanism}
\label{subsec_accuracy_lap}
Accuracy bound for Laplace mechanism is provided by its probability density function:
\begin{equation*}
Pr[|Y| \geq t] = e^{- \frac{t}{b}},
\end{equation*}
where $Y \sim Lap(b)$, $b = \frac{\Delta \bysinfer}{\epsilon}$ in our case.

@@

\subsubsection{Accuracy Bound for Improved Laplace Mechanism}
\label{subsec_accuracy_lap}
Accuracy bound for improved Laplace mechanism is obtained from the standard Laplace Mechanism by replacing the sensitivity of $\Delta \bysinfer$ with $2$.
\[
Pr[\lfloor Y \rfloor = t] = Pr[ t-1 \leq Y < t] = \frac{1}{2} (e^{- \frac{\epsilon (t - 1)}{2}} - e^{- \frac{\epsilon (t)}{2}}).
\]

@@

\section{Conclusion and Future Work}
From what we have seen in the previous sections we can obtain some preliminary conclusions. That is, the probabiliy measure approach outperforms the $\ell_1$-norm approach in the following cases:

\begin{enumerate}
	\item  $\hexpmech$ outperforms the baseline approach but not the improved one, for priors with small parameters.
  	\item When the prior parameters increase $\hexpmech$ is comparable with the improved baseline approach.
\end{enumerate}
